New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification

### 2025-08-13 intro.tex
Explaining wlw abbreviation

Our approach to the problem is to evaluate practical performance of different 
methods to aggregate probabilistic binary predictions. Such methods---called coupling methods---first appeared in work of \cite{refregier1991probabilistic} when making 
multi-class classification using neural networks. 
Many authors followed with alternative proposals 
\cite{price1994pairwise, hastie1998classification,  zahorian1999partitioned,
wu2004probability, vsuch2015new, vsuch2016bayes}.

>>>>

Our approach to the problem is to evaluate practical performance of different 
methods to aggregate probabilistic binary predictions. Such methods---called coupling methods---first appeared in work of \cite{refregier1991probabilistic} when making 
multiclass classification using neural networks. 
Many authors followed with alternative proposals 
\cite{price1994pairwise, hastie1998classification,  zahorian1999partitioned,
wu2004probability, vsuch2015new, vsuch2016bayes}.
